---
title: "gmxdcc: GARCH-MIDAS and DCC-MIDAS with covariates and breaks"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{gmxdcc: GARCH-MIDAS and DCC-MIDAS with covariates and breaks}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = FALSE)
```

## Model overview

The univariate model is the two-component GARCH-MIDAS
\[
r_t = \mu + \sqrt{\tau_t\, g_t}\,\epsilon_t, \qquad
g_t = (1-\alpha-\beta) + \alpha \frac{(r_{t-1}-\mu)^2}{\tau_{t-1}} + \beta g_{t-1},
\]
with a slowly-moving long-run component driven by low-frequency covariates
\[
\log \tau_t = m(t) + \sum_j \theta_j(t)\,\mathrm{MIDAS}(X_j; \omega_j)_t .
\]

Any number of covariates \(X_j\) is allowed (monthly or quarterly), each
with its own MIDAS lag order; realized volatility computed from the daily
returns themselves can be included with `rv = TRUE`. When `break_dates`
are supplied, the intercept \(m\) and every slope \(\theta_j\) become
piecewise-constant across the regimes defined by the break dates.

The multivariate step models the conditional correlation of the
standardized residuals: cDCC, aDCC, DECO, or DCC-MIDAS with a long-run
correlation driven by realized correlations (`rc`), exogenous covariates
(`corr_X`) and optional breaks (`corr_break_dates`).

## Bundled sample data

The package ships four small datasets so the examples run as-is:

* `topix_market` — daily TOPIX market returns (column `TOPIX`);
* `topix_autos` — daily TOPIX-17 Autos & Transportation Equipment industry
  returns (column `AUTOS`);
* `jp_macro_uncertainty` — monthly standardized Japan macro uncertainty
  index (column `JPMU`);
* `jp_mu_breaks` — the four structural break dates detected in the mean of
  `jp_macro_uncertainty` with `strucchange::breakpoints(y ~ 1)`, ready to
  use as `break_dates` / `corr_break_dates`.

包内置四个示例数据集(TOPIX 市场收益、汽车行业收益、日本宏观不确定性
指数及其结构突变日期),下述示例可直接运行。

## Univariate example

Market volatility with a macro-uncertainty-driven long-run component and
structural breaks:

```{r univ}
library(gmxdcc)
library(xts)

fit <- fit_garch_midas(
  topix_market,
  X = list(JPMU = jp_macro_uncertainty),  # any number of macro covariates
  K = 24,                                 # lag order (vector for several X)
  rv = FALSE,                             # TRUE adds realized volatility
  break_dates = jp_mu_breaks,             # piecewise m(t) and theta(t)
  distribution = "norm", lag_fun = "Beta", period = "monthly",
  seed = 1
)
summary(fit)
coef(fit); logLik(fit); vcov(fit)

# Long-run vs total conditional volatility / 长期成分与总条件波动率
plot(xts(cbind(total = fit$est_vol_in_s, longrun = sqrt(fit$est_lr_in_s)),
         order.by = seq_along(fit$est_vol_in_s)))
```

## Two-step DCC-MIDAS example

Conditional correlation between the autos industry and the market, with
the long-run correlation driven by macro uncertainty and its breaks:

```{r dcc}
panel <- merge.xts(topix_autos, topix_market)
panel <- panel[complete.cases(panel), ]

dcc <- fit_dcc(
  panel,
  univariate = "garch_midas",
  univariate_args = list(X = jp_macro_uncertainty, K = 24, rv = FALSE,
                         break_dates = jp_mu_breaks),
  correlation = "DCC-MIDAS",
  rc = FALSE,                       # set TRUE (+ N_c) to add realized corr
  corr_X = list(JPMU = jp_macro_uncertainty), K_c = 24,
  corr_break_dates = jp_mu_breaks,
  seed = 1
)
summary(dcc)
dim(dcc$R_t)      # in-sample conditional correlations

# Conditional correlation path / 条件相关系数路径
plot(xts(dcc$R_t[1, 2, ], order.by = dcc$Days))
```

With `out_of_sample = n` the same call additionally returns `R_t_oos`,
`H_t_oos` etc. for the held-out days, produced by the warm-started
full-sample filter.

## Migration from the legacy script

| Legacy model string | New arguments |
|---|---|
| `GM_noskew_RV` | `rv = TRUE, X = NULL` |
| `GM_noskew_X` | `rv = FALSE, X = list(x)` |
| `GM_noskew_RV_X` | `rv = TRUE, X = list(x)` |
| `GM_noskew_*_sb` | add `break_dates` |
| `DCCMIDAS_RC` | `correlation = "DCC-MIDAS", rc = TRUE` |
| `DCCMIDAS_X` | `correlation = "DCC-MIDAS", rc = FALSE, corr_X = list(x)` |
| `DCCMIDAS_RC_X` | `correlation = "DCC-MIDAS", rc = TRUE, corr_X = list(x)` |
| `DCCMIDAS_*_sb` | add `corr_break_dates` |

Argument renames: `X_stru_break_date_vec` → `break_dates` /
`corr_break_dates`; `type` → `period`; `R` → `n_starts`.

## Standard errors

Both steps report Bollerslev–Wooldridge (1992) QMLE sandwich standard
errors \(H^{-1}(G'G)H^{-1}\) computed from the numerical Hessian and the
outer product of per-observation gradients. As is standard in the two-step
DCC literature (Engle 2002), the second-step standard errors do not correct
for first-stage estimation uncertainty.

## Out-of-sample design

With `out_of_sample = n`, parameters are estimated on the first
\(T - n\) observations only. All conditional quantities for the held-out
days come from filtering the **full** sample with the frozen parameter
estimates, so the recursions continue from the last in-sample state
(the legacy script restarted them cold), and unconditional targets
(covariance/asymmetry matrices) are computed from in-sample residuals only.

## Parallel use

Where the legacy project kept a separate "multi cores" copy of the script,
simply attach the package inside each worker:

```{r par}
parallel::clusterEvalQ(cl, library(gmxdcc))
```
